---
title: "Lab 00 - Hello IDS!"
author: "NOR DANISH RAZIQ NOR AZHAR"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("moses", "andrew", "grace", 
           "divyam", "khushi"),
  github_username = c("Mosesweintraub", "andrewrightjames", "grxcetait", 
                      "DivyamAneja", "khushiwadhwa0210"), 
  colour = c("red", "blue", "lightgreen", 
             "blue", "red"),
  hobby = c("rowing", "rowing", "reading", 
            "cricket", "annoyingpeople"),
  favourite_number = c(9, 2, 1, 7, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data.

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

It shows the favourite numbers and the usernames of each team member while also using their favourite colour as the indicator

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "favourite_number_github_username")
```

The code "labs()" allows the user to plot graphs and edit the axis and titles

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Too much data it will look too clustered